---
title: 'Investigating NASA fireballs'
author: "Jason Lee"
output: html_document
---



## Understanding the Data
We'll work with a dataset that shows when and where fireballs have been seen. Dataset is acquired from NASA the center of sensors.

Columns:

1. date - time fireball seen
2. energy - energy of joules
3. impact_e - total impact energy
4. lat - latitude
5. lat_dir - latitude direction
6. lon - longitude
7. lon_dir - longitude direction
8. alt - altitude
9. vel - velocity of fireball in KM per second



```{r message=FALSE}
library("shinydashboard")
library("shiny")
library("readr")

nasa_filepath <- ("cneos_fireball_data.csv")
nasa_fireball <- read.csv(nasa_filepath)

```

## Explore data
```{r}
# Print the nasa_fireball data frame
print(head(nasa_fireball))
```

```{r}
# Examine the types of variables present
#nasa_fireball$energy <- as.numeric(nasa_fireball$energy)
sapply(nasa_fireball, class)

```

```{r}
# Observe the number of observations in this data frame
nrow(nasa_fireball)
```

```{r}
# Check for missing data
sapply(nasa_fireball,anyNA)
```

## Build Dashboard

### Value boxes
First, I'll create a value boxs showing the maximum values for velocity, energy and impact energy.

```{r}

max_impact_e <- max(nasa_fireball$impact_e, na.rm = TRUE)
max_vel <- max(nasa_fireball$vel, na.rm = TRUE)
max_energy <- max(nasa_fireball$energy, na.rm = TRUE)

body <- dashboardBody(
  fluidRow(
    # Add a value box for maximum energy
    valueBox(
      value = max_energy,
      subtitle = "Maximum total radiated energy (Joules)",
      icon = icon("lightbulb-o"),
      color = "green"
    ),
    valueBox(
      value = max_impact_e, 
      subtitle = "Maximum impact energy (kilotons of TNT)",
      icon = icon("star"),
      color = "yellow"
    ),
    valueBox(
      value = max_vel,
      subtitle = "Maximum pre-impact velocity", 
      icon = icon("fire"),
      color = "red"

    )
  )
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
)
#server function
server <- function(input, output) {}

shinyApp(ui, server)
```



# Building a map to visualize the fireballs
```{r}
library("leaflet")

server <- function(input, output) {
  output$plot <- renderLeaflet({
    leaflet() %>%
      addTiles() %>%  
      addCircleMarkers(lng = nasa_fireball$lon, lat = nasa_fireball$lat, radius = log(nasa_fireball$impact_e), label = nasa_fireball$date, weight = 2)
    })
}

body <- dashboardBody( 
 leafletOutput("plot")
)

ui <- dashboardPage(
  header = dashboardHeader(),
  sidebar = dashboardSidebar(),
  body = body
)

shinyApp(ui, server)

```

## Putting whole dashboard together
```{r}
library("leaflet")

server <- function(input, output) {
  output$plot <- renderLeaflet({
    leaflet() %>%
      addTiles() %>%  
      addCircleMarkers(
        lng = nasa_fireball$lon,
        lat = nasa_fireball$lat, 
        radius = log(nasa_fireball$impact_e), 
        label = nasa_fireball$date, 
        weight = 2)
    })
}

body <- dashboardBody(
 fluidRow(
   valueBox(
      value = max_energy,
      subtitle = "Maximum total radiated energy (Joules)",
      icon = icon("lightbulb-o"),
      color = "green"
    ),
    valueBox(
      value = max_impact_e, 
      subtitle = "Maximum impact energy (kilotons of TNT)",
      icon = icon("star"),
      color = "yellow"
    ),
    valueBox(
      value = max_vel,
      subtitle = "Maximum pre-impact velocity", 
      icon = icon("fire"),
      color = "red"
    ) 
  ),
  fluidRow(
    leafletOutput("plot")
  )
)


ui <- dashboardPage(
  skin = "blue",
  header = dashboardHeader(),
  sidebar = dashboardSidebar(),
  body = body
)

shinyApp(ui, server)

```

